---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Surface Mass Balance Data

Preview this [Data Package](http://specs.frictionlessdata.io/data-packages/) using the [Data Package Viewer](http://data.okfn.org/tools/view?url=https://github.com/columbia-glacier/mass-balance).

## Data

<details><summary>View metadata (<i>datapackage.json</i>)</summary>
```{r, echo=FALSE, results="asis"}
txt <- dpkg::as_markdown(dpkg:::read_meta())
cat(txt)
```
</details>

### Description

Annual surface mass balance measurements compiled from the 1978 campaign [sources/mayo-and-others-1979.pdf](sources/mayo-and-others-1979.pdf) and the 2010-2011 campaign [sources/oneel-2012.pdf](sources/oneel-2012.pdf).

### Citations

> Shad O'Neel (2012). Surface Mass Balance of the Columbia Glacier, Alaska, 1978 and 2010 Balance Years. U.S. Geological Survey Data Series 676. Retrieved from http://pubs.er.usgs.gov/publication/ds676. Archived at [sources/oneel-2012.pdf](sources/oneel-2012.pdf).

> Larry R. Mayo, D. C. Trabant, Rod March, and Wilfried Haeberli (1979). Columbia Glacier Stake Location, Mass Balance, Glacier Surface Altitude, and Ice Radar Data, 1978 Measurement Year. U.S. Geological Survey Open File Report 79–1168. Online at https://pubs.er.usgs.gov/publication/ofr791168. Archived at [sources/mayo-and-others-1979.pdf](sources/mayo-and-others-1979.pdf).

## To Do

- GPS coordinates of the 2011 TazDivide site.
